\documentclass[../paper.tex]{subfiles}
\begin{document}

    Bloom filters and other approximate membership query data structures, or
    AMQs, are often used to help avoid costly lookups to large dictionaries.
    They achieve this by keeping a compact representation of a set
    $S$ of keys from a universe $U$.  All AMQs support inserts and lookups
    while some also support deletes.  When performing a lookup for an item $x$
    that has been inserted, i.e. $x\in S$, the AMQ is guaranteed to return
    {\it present}.  The downside of their compact representation of $S$ is
    that, when a lookup is performed for an item $x \notinS$, {\it present}
    may be returned with probability $\epsilon$.  This {\bf false-positive
    probability} is a usually a tunable parameter with a lower $\epsilon$
    typically requiring more space to be used by the AMQ.  That said, their
    compact representation is also what makes them helpful since they can be
    kept in memory or on a local machine and queried locally to avoid having to
    access disk or another machine over a network.  As such, two of the primary
    concerns when analyzing an AMQ are then, how often does it return
    false-positives and how much space does it require to do so?

    The majority of current AMQs only offer strong guarantees for independent
    queries, but the false-positive probability rate for most of these can be
    pushed toward 1 given the right sequence of queries.  In the adversarial
    case, this can be done by repeated lookups of elements that result in
    false-positives, but, even in regular workloads, the lack of strong
    guarantees for sequences of lookups can lead to poor performance depending
    on the circumstances.  For example, Mitzenmacher et al.
    \cite{adaptive-cuckoo} discuss how repeated lookups can arise during packet
    processing because the lookups may correspond to flow identifiers.  Their
    solution to this problem was to create a variant of the Cuckoo Filter
    \cite{cuckoo-filter} which adapts to false positives by removing them for
    future queries and show using simulations that this does indeed result in a
    better false positive rate under such circumstances.  Bender et al.
    \cite{broom-filter} take a similar approach in designing the Broom Filter
    which is a variant of the Quotient Filter \cite{quotient-filter} that also
    adapts to false positives, but rather than showing their advantages through
    simulations, they define an {\bf adaptive} AMQ as one that maintains a
    false-positive probability of $\epsilon$ for each query regardless of the
    answers to previous queries and show that the Broom Filter is proveably
    adaptive.

    We first discuss previous attempts at adaptivity, such as the bloomier filter
    and the retouched bloom filter. Then, we focus on the adaptive cuckoo filter
    and the broom filter. We study the theory for designing adaptive filters and
    compare the two filters' theoretical guarantees and practical performance.
    Through a long endeavor to implement the broom filter, we find concerns about
    the broom filter that makes it impractical. In other words, adaptive cuckoo
    filter is currently the most practical solution for adaptive AMQs.
\end{document}
